---
title: 'Default Config'
date: '`r format(Sys.Date())`'
output:
  html_document:
    toc: yes
    toc_float: yes
    toc_depth: 3
    number_sections: yes
    css: defaultConfig.css
---


```{r}
cfg <- list()
cfg$gms <- list()
```




# R Parameters




## General


### title {-}

title of the actual run

```{r}
cfg$title <- "default"
```

**Possible Values:**

--

**Description:**

--



### description {-}

short description of the run

```{r}
cfg$description <- "REMIND run with default settings"
```

**Possible Values:**

--

**Description:**

--



### regionmapping {-}

region settings

```{r}
cfg$regionmapping <- "config/regionmappingH12.csv"
```

**Possible Values:**

--

**Description:**

--



### inputRevision {-}

Current input data revision (<mainrevision>.<subrevision>)

```{r}
cfg$inputRevision <- 6.288
```

**Possible Values:**

--

**Description:**

--



### CESandGDXversion {-}

Current CES parameter and GDX revision (commit hash)

```{r}
cfg$CESandGDXversion <- "151402067096f94a7abc308b65ba1119ab40cdd4"
```

**Possible Values:**

--

**Description:**

--



### force_download {-}

Force the model to download new input data

```{r}
cfg$force_download <- FALSE
```

**Possible Values:**

--

**Description:**

--



### force_replace {-}

Should an existing output folder be replaced if a new run with the same name is started?

```{r}
cfg$force_replace <- FALSE
```

**Possible Values:**

--

**Description:**

--



### runstatistics {-}

Folder run statistics should be submitted to

```{r}
cfg$runstatistics <- "/p/projects/rd3mod/models/statistics/remind"
```

**Possible Values:**

--

**Description:**

--



### magicc_template {-}

Folder containing magcicc files that can not be published open source. These files are automatically
copied into remind when starting a run and required to calcualte climate responses (e.g. temperature).

```{r}
cfg$magicc_template <- "/p/projects/rd3mod/magicc/"
```

**Possible Values:**

--

**Description:**

--



### model_name {-}

name of the overall model (used for input data and run statistics)
should usually not be changed

```{r}
cfg$model_name <- "REMIND"
```

**Possible Values:**

--

**Description:**

--



### validationmodel_name {-}

name of the validation folder for this model (used for historical and validation data)
should usually not be changed

```{r}
cfg$validationmodel_name <- "VALIDATIONREMIND"
```

**Possible Values:**

--

**Description:**

--



### model_version {-}

model version of the overall model (used for run statistics only).
Use extension "-rc" for release candidate and "-dev" for developer version

```{r}
cfg$model_version <- "2.2-dev"
```

**Possible Values:**

--

**Description:**

--



### gamsv {-}

Choose which GAMS version to use (choosing the default option "gams" uses the GAMS system in your PATH variable - in both UNIX and Windows)
Cluster Example: if you want GAMS version 24.0, use "/p/system/packages/gams/24.0.1/gams"
Local machine Example: use your GAMS path, e.g. "C:\\GAMS\\win32\\24.3\\gams.exe" (please note the double backslashes)

```{r}
cfg$gamsv <- "gams"
```

**Possible Values:**

--

**Description:**

--



### action {-}

Action that should be performed ("ce": compile and run, "c": compile)

```{r}
cfg$action <- "ce"
```

**Possible Values:**

--

**Description:**

--



### tarball_puts {-}

Tar-ball all the put files to save space?

```{r}
cfg$tarball_puts <- "on"
```

**Possible Values:**

--

**Description:**

--



### slurmConfig {-}

Provide additional SLURM parameters (e.g. "--time=03:30:00") not included in
the list of following parameters that are set automatically in start.R:
--qos, --nodes, --tasks-per-node, -job-name, --output, --mail-type, --comment.

```{r}
cfg$slurmConfig <- ""
```

**Possible Values:**

--

**Description:**

--



### logoption {-}

Should REMIND output be shown in console? (0:no, 2:logfile, 3:yes)

```{r}
cfg$logoption <- 2
```

**Possible Values:**

--

**Description:**

--



### output {-}

Just list the name of the output scripts that should be used by output.R
At the moment there are several R-scripts located in scripts/output/

```{r}
cfg$output <- c("reporting","reportCEScalib","rds_report")
```

**Possible Values:**

--

**Description:**

--



### results_folder {-}

Set the format for the results folder, type string :date: in order to use the current time stamp in the folder name (e.g. "results:date:") use :title: to use the current title in the folder name

```{r}
cfg$results_folder <- "output/:title::date:"
```

**Possible Values:**

--

**Description:**

--



### files2export {-}

Which files should be copied into the output folder?

```{r}
cfg$files2export <- list()
```

**Possible Values:**

--

**Description:**

--



### converted_input_folder {-}

There is the converted data located?

```{r}
cfg$converted_input_folder <- "config"
```

**Possible Values:**

--

**Description:**

--



### RunsUsingTHISgdxAsInput {-}

placeholder for storing information on subsequent runs that need input from this run

```{r}
cfg$RunsUsingTHISgdxAsInput <- character(0)
```

**Possible Values:**

--

**Description:**

--





# Modules




## General


### 01_macro {-}

--

```{r}
cfg$gms$macro <- "singleSectorGr"
```

**Possible Values:** 

* `"singleSectorGr"`:

**Description:** 

--



### 02_welfare {-}

--

```{r}
cfg$gms$welfare <- "utilitarian"
```

**Possible Values:** 

* `"utilitarian"`:

**Description:** 

--



### 04_PE_FE_parameters {-}

--

```{r}
cfg$gms$PE_FE_parameters <- "iea2014"
```

**Possible Values:** 

* `"iea2014"`: new PE-FE parameters based on IEA 2014

**Description:** 

--



### 05_initialCap {-}

--

```{r}
cfg$gms$initialCap <- "on"
```

**Possible Values:** 

* `"on"`:      load existing CES parameters matching model configuration

**Description:** 

--



### 11_aerosols {-}

--

```{r}
cfg$gms$aerosols <- "exoGAINS"
```

**Possible Values:** 

* `"exoGAINS"`   :

**Description:** 

--



### 15_climate {-}

--

```{r}
cfg$gms$climate <- "off"
```

**Possible Values:** 

* `"off"`: no climate coupling
* `"magicc"`: MAGICC - iterative mode, outside of optimization.
* `"box"`: Petschel-Held

**Description:** 

--



### 16_downscaleTemperature {-}

--

```{r}
cfg$gms$downscaleTemperature <- "off"
```

**Possible Values:** 

* `"off"`
* `"CMIP5"`: downscale GMT to regional temperature based on CMIP5 data (between iterations, no runtime impact). Requires climate='magicc' and cm_rcp_scen={rcp26,rcp85}

**Description:** 

--



### 20_growth {-}

--

```{r}
cfg$gms$growth <- "exogenous"
```

**Possible Values:** 

* `"exogenous"`: exogenous growth
* `"endogenous"`: endogenous growth !!Warning: still experimental stuff!!
* `"spillover"`: endogenous growth with spillover externality !!Warning: not yet calibrated!!

**Description:** 

--



### 21_tax {-}

--

```{r}
cfg$gms$tax <- "on"
```

**Possible Values:** 

* `"on"`: tax mechanism active
* `"off"`: no tax mechanism

**Description:** 

--



### 22_subsidizeLearning {-}

--

```{r}
cfg$gms$subsidizeLearning <- "off"
```

**Possible Values:** 

* `"globallyOptimal"`: Only works with Nash, gives cooperative solution w.r.t. the learning spillover - this should then be equivalent to the Negishi solution.
* `"off"`: do not subsidize learning. Default setting for Negishi. With Nash, this gives the non-cooperative solution w.r.t. the learning spillover.

**Description:** 

--



### 23_capitalMarket {-}

--

```{r}
cfg$gms$capitalMarket <- "debt_limit"
```

**Possible Values:** 

* `"imperfect"`: Imperfect capital market: brings initial consumption shares closer to empirical data
* `"perfect"`:   Perfect capital market (results in large short-term capital flows from North to South)
* `"debt_limit"`: Weak imperfection of capital market by debt and surplus growth limits

**Description:** 

--



### 24_trade {-}

--

```{r}
cfg$gms$trade <- "standard"
```

**Possible Values:** 

* `"standard"`:

**Description:** 

--



### 26_agCosts {-}

--

```{r}
cfg$gms$agCosts <- "costs"
```

**Possible Values:** 

* `"off"`: agricultural costs zero, no trade taken into account
* `"costs"`: includes total landuse costs
* `"costs_trade"`: includes agricultural production costs and the MAgPIE trade balance

**Description:** 

--



### 29_CES_parameters {-}

--

```{r}
cfg$gms$CES_parameters <- "load"
```

**Possible Values:** 

* `"load"`:      load existing CES parameters matching model configuration
* `"calibrate"`: calculate new CES parameters based on v_cesIO trajectories -- under development!

**Description:** 

--



### 30_biomass {-}

--

```{r}
cfg$gms$biomass <- "magpie_40"
```

**Possible Values:** 

* `"exogenous"`:     exogenous biomass extraction and costs
* `"magpie_40"`: using supplycurved derived from MAgpIE 4.0

**Description:** 

--



### 31_fossil {-}

--

```{r}
cfg$gms$fossil <- "grades2poly"
```

**Possible Values:** 

* `"timeDepGrades"`: time-dependent grade stucture of fossil resources (oil & gas only)
* `"grades2poly"`  : simplified version of the time-dependent grade realization (using polynomial functions)
* `"exogenous"`    : exogenous fossil extraction and costs

**Description:** 

--



### 32_power {-}

--

```{r}
cfg$gms$power <- "IntC"
```

**Possible Values:** 

* `"IntC"`	:	Power sector formulation with Integration Cost (IntC) markups and curtailment for VRE integration - linearly increasing with VRE share -, and fixed capacity factors for dispatchable power plants
* `"RLDC"`	:	Power sector formulation with Residual Load Duration Curve (RLDC) formulation for VRE power integration, and flexible capacity factors for dispatchable power plants
* `"DTcoup"`    : Power sector formulation with coupling to DIETER

**Description:** 

--



### 33_CDR {-}

--

```{r}
cfg$gms$CDR <- "DAC"
```

**Possible Values:** 

* `"off"`        : no carbon dioxide removal technologies except BECCS
* `"weathering"` : includes enhanced weathering
* `"DAC"` : 	   includes direct air capture
* `"all"` : 	   includes all CDR technologies

**Description:** 

--



### 35_transport {-}

--

```{r}
cfg$gms$transport <- "edge_esm"
```

**Possible Values:** 

* `"complex"`:  transport realization including electricity in the transport sector (*RP*)
* `"edge_esm"`: transport realization with detailed modes/vehicles representation (*AD*, *MR*)

**Description:** 

--



### 36_buildings {-}

--

```{r}
cfg$gms$buildings <- "simple"
```

**Possible Values:** 

* `"simple"`: representation of the demand in terms of energy carriers
* `"services_with_capital"`: representation of the demand by energy service with capital
* `"services_putty"`: representation of the demand by energy service with capital and with putty-clay for buildings insulation

**Description:** 

--



### 37_industry {-}

--

```{r}
cfg$gms$industry <- "subsectors"
```

**Possible Values:** 

* `"fixed_shares"`: fixed shares of industry sub-sectors (cement, chemicals,
steel, other) in industry FE use
* `"subsectors"`:   models industry subsectors explicitly with individual CES nests
for cement, chemicals, steel, and otherInd production.

**Description:** 

--



### 39_CCU {-}

--

```{r}
cfg$gms$CCU <- "on"
```

**Possible Values:** 

* `"on"`: simple representation of carbon capture and utilization technologies, first only example of syngas (H22CH4)
* `"off"`: no representation of carbon caputre and utilization technologies.

**Description:** 

--



### 40_techpol {-}

--

```{r}
cfg$gms$techpol <- "none"
```

**Possible Values:** 

* `"none"`: no technology policies
* `"lowCarbonPush"`: [works only with Negishi] global low-carbon push until 2030: PV, CSP, Wind, Gas-CCS, Bio-CCS and Electromobility
* `"coalPhaseout"`: [works only with Negishi] global phase-out of new freely-emitting coal conversion, caps all coal routes with the exception of coaltr: coal solids can still expand
* `"coalPhaseoutRegional"`: [works only with Negishi] global phase-out of new freely-emitting coal conversion, caps all coal routes with the exception of coaltr: coal solids can still expand
* `"CombLowCandCoalPO"`: [works only with Negishi] combination of lowCarbonPush and coalPhaseout
* `"NDC"`: Technology targets for 2030 for spv,wind,tnrs.
* `"NPi"`: Reference technology targets, mostly already enacted (N)ational (P]ol(i)cies, mostly for 2020
* `"EVmandates"`: mandate for electric vehicles - used for UBA project

**Description:** 

--



### 41_emicapregi {-}

--

```{r}
cfg$gms$emicapregi <- "none"
```

**Possible Values:** 

* `"none"`: no regional emission caps
* `"CandC"`:  contraction and convergence allocation (under construction)
* `"GDPint"`:  GDP intensity allocation (under construction)
* `"POPint"`:  sovereignity (per cap.) allocation (under construction)
* `"exog"`:   exogenous emission cap path (generic)  (under construction)
* `"PerCapitaConvergence"`:   based on CandC: convergence, to be run with emiscen = 4
* `"AbilityToPay"`:   mitigation requirement shared based on per-capita GDP, to be run with emiscen = 4

**Description:** 

--



### 42_banking {-}

--

```{r}
cfg$gms$banking <- "off"
```

**Possible Values:** 

* `"off"`: no banking and borrowing of emission permits, no when-flexibility
* `"banking"`:  only banking allowed, no borrowing at all

**Description:** 

--



### 45_carbonprice {-}

--

```{r}
cfg$gms$carbonprice <- "none"
```

**Possible Values:** 

* This module defines the carbon price pm_taxCO2eq, with behaviour across regions governed by similar principles (e.g. global targets, or all following NDC or NPi policies).
* `"none"`: no tax policy (combined with all emiscens except emiscen eq 9)
* `"exponential"`: 5% exponential increase over time of the tax level in 2020 set via cm_co2_tax_2020 (combined with emiscen eq 9 and cm_co2_tax_2020>0)
* `"expoLinear"`: 5% exponential increase until c_expoLinear_yearStart, linear increase thereafter
* `"exogenous"`: carbon price is specified using an external input file or using the switch cm_regiExoPrice
* `"linear"`: linear increase over time of the tax level in 2020 set via cm_co2_tax_2020 (combined with emiscen eq 9 and cm_co2_tax_2020>0)
* `"diffPriceSameCost"` ! experimental ! adjusts regional carbon prices until regional mitigation costs (in NPV GDP) are equal across regions. Use with iterative_adjust=2, emiscen=9. Experimental feature, you are responsible to check for convergence yourself (check that p45_mitiCostRel is about constant over iterations)
* `"temperatureNotToExceed"`: [test and verify before using it!] Find the optimal carbon carbon tax (set cm_emiscen=9) for the not-to-exceed temperature target defined by cm_carbonprice_temperatureLimit.
* `"NDC2constant"`: linearly phase in global constant price from NDC prices (default 2020-2040 phase-in)
* `"diffCurvPhaseIn2Lin"`: [REMIND 2.1 default for validation peakBudget runs, in combination with "iterative_target_adj" = 9] curved convergence of CO2 prices between regions until cm_CO2priceRegConvEndYr; developed countries have linear path from 0 in 2010 through cm_co2_tax_2020 in 2020;
* `"diffPhaseIn2Constant"`: !experimental! linearly phase in global constant price, with starting values differentiated by GDP/cap
* `"NDC"`: implements a carbon price trajectory consistent with the NDC targets (up to 2030) and a trajectory of comparable ambition post 2030 (1.25%/yr price increase and regional convergence of carbon price). Choose version using cm_NDC_version "2022_cond", "2022_uncond", or replace 2022 by 2021 or 2018 to get all NDC published until end of these years.

**Description:** 

--



### 46_carbonpriceRegi {-}

--

```{r}
cfg$gms$carbonpriceRegi <- "none"
```

**Possible Values:** 

* This module applies a markup pm_taxCO2eqRegi on top of pm_taxCO2eq to achieve additional intermediate targets.
* `"none"`: no regional carbonprice policies
* `"NDC"`: implements a carbon price markup trajectory consistent with the NDC targets between 2030 and 2070
* `"netZero"`: implements a carbon price markup trajectory consistent with the net zero targets

**Description:** 

--



### 47_regipol {-}

--

```{r}
cfg$gms$regipol <- "none"
```

**Possible Values:** 

* The regiCarbonPrice realisation defines more detailed region or emissions market specific targets, overwriting the behaviour of pm_taxCO2eq and pm_taxCO2eqRegi for these regions.
* `"none"`: no regional policies
* `"regiCarbonPrice"`: Region specific or region group independent carbon price.
* the target is defined in the cm_regiCO2target switch, for year target e.g. "2050.EUR.year.netCO2 0.7, 2050.USA.year.grossFFaI 1.0" sets a 0.7GtCO2 net CO2 target for EUR in 2050 and a 1GtCO2 gross Fossil Fuel and Industry CO2 emissions target for USA
* for budget target: "2050.EUR.budget.netCO2 70, 2050.USA.budget.grossFFaI 100" sets a netCO2/grossFFaI budget from 2020-2050 correspondingly (note: don't put values to 0 as this will make the model ignore the switch)

**Description:** 

--



### 50_damages {-}

--

```{r}
cfg$gms$damages <- "off"
```

**Possible Values:** 

* `"off"`: no damages on GDP
* `"DiceLike"`: DICE-like damages (linear-quadratic damages on GDP). Choose specification via cm_damage_DiceLike_specification
* `"BurkeLike"`: Burke-like damages (growth rate damages on GDP). Choose specification via cm_damage_BurkeLike_specification and cm_damage_BurkeLike_persistenceTime
* `"KWLike"`: Damage function based on Kalkuhl & Wenz (2020)

**Description:** 

--



### 51_internalizeDamages {-}

--

```{r}
cfg$gms$internalizeDamages <- "off"
```

**Possible Values:** 

* `"off"`:
* `"DiceLikeItr"`: Internalize DICE-like damages (calculate the SCC) adjust cm_damages_SccHorizon. Requires cm_emiscen=9 for now.
* `"BurkeLikeItr"`: Internalize Burke-like damages (calculate the SCC) adjust cm_damages_SccHorizo. Requires cm_emiscen=9 for now.
* `"KWlikeItr"`: Internalize damage function based on Kalkuhl & Wenz (2020). Requires cm_emiscen=9 for now.

**Description:** 

--



### 70_water {-}

--

```{r}
cfg$gms$water <- "off"
```

**Possible Values:** 

* `"off"`: no water demand taken into account
* `"exogenous"`: exogenous water demand is calculated based on data on water demand coefficients and cooling shares
* `"heat"`: as exogenous only that vintage structure in combination with time dependent cooling shares as vintages and efficiency factors are also considered and demand is a function of excess heat as opposed to electricity output

**Description:** 

--



### 80_optimization {-}

--

```{r}
cfg$gms$optimization <- "nash"
```

**Possible Values:** 

* `"nash"`: Nash solution. Adjust cm_nash_autoconverge to needs.
* `"negishi"`: calculates a Negishi solution (social planner)
* `"testOneRegi"`:  solves the problem for one region for given prices (taken from gdx).
*                ! Warning:  For development purposes only !

**Description:** 

--



### 81_codePerformance {-}

--

```{r}
cfg$gms$codePerformance <- "off"
```

**Possible Values:** 

* `"off"`: nothing happens
* `"on"`:  test code performance: noumerous (30) succesive runs performed in a triangle, tax0, tax30, tax150, all growing exponentially,
therefore use carbonprice|exponential, c_emiscen|9, and cm_co2_tax_2020|0.

**Description:** 

--





# GAMS Switches




## General


### cm_iteration_max {-}

number of Negishi iterations

```{r}
cfg$gms$cm_iteration_max <- 1
```

**Possible Values:**

--

**Description:**





### c_solver_try_max {-}

maximum number of inner iterations within one Negishi iteration (<10)

```{r}
cfg$gms$c_solver_try_max <- 2
```

**Possible Values:**

--

**Description:**

*** Careful: for each inner_itr_count, the size of remind.lst can increase by 50MB!



### c_keep_iteration_gdxes {-}

save intermediate iteration gdxes

```{r}
cfg$gms$c_keep_iteration_gdxes <- 0
```

**Possible Values:**

--

**Description:**

NA



### cm_nash_autoconverge {-}

choice of nash convergence mode

```{r}
cfg$gms$cm_nash_autoconverge <- 1
```

**Possible Values:**

* (0): manually set number of iterations by adjusting [cm_iteration_max]
* (1): run until solution is sufficiently converged  - coarse tolerances, quick solution.  ! donot use in production runs !
* (2): run until solution is sufficiently converged  - fine tolerances, for production runs.

**Description:**

--



### cm_emiscen {-}

policy scenario choice

```{r}
cfg$gms$cm_emiscen <- 1
```

**Possible Values:**

* (0): no global budget. Policy may still be prescribed by 41_emicaprei module.
* (1): BAU
* (2): temperature cap
* (3): CO2 concentration cap
* (4): emission time path
* (5): forcing target from 2010 (not to exceed)
* (6): budget
* (8): forcing target from 2100 onwards (overshoot scen)
* (9): tax scenario (requires running module [21_tax] "on"), tax level controlled by module [45_carbonprice] and [cm_co2_tax_2020], other ghg etc. controlled by [cm_rcp_scen]

**Description:**

*RP* WARNING: [cm_emiscen] 3 should not be used anymore, as the MACs are not updated anymore.
*JeS* WARNING: data for [cm_emiscen] 4 only exists for multigas_scen 2 bau scenarios and for multigas_scen 1



### cm_iterative_target_adj {-}

whether or not a tax or a budget target should be iteratively adjusted depending on actual emission or forcing level

```{r}
cfg$gms$cm_iterative_target_adj <- 0
```

**Possible Values:**

* (0): no iterative adjustment
* (2): iterative adjustment II based on magicc calculated forcing (for both budget and tax runs), see modules/climate/magicc/postsolve.gms for direct algorithms of adjustment
* (3): [requires [45_carbonprice] = "NDC" and emiscen = 9] iterative adjustment III for tax based on 2025 or 2030 regionally differentiated emissions, see module/[45_carbonprice]/<NDC/NPi2018>/postsolve.gms for algorithm of adjustment
* (4): iterative adjustment IV for both budget and tax runs based on CO2 FF&I emissions 2020-2100, see core/postsolve.gms for direct algorithms of adjustment
* (5): iterative adjustment V for both budget and tax runs based on CO2 emissions 2020-2100, see core/postsolve.gms for direct algorithms of adjustment
* (6): iterative adjustment VI for both budget and tax runs based on peak CO2 emissions budget, without changing temporal profile (i.e. with overshoot), see core/postsolve.gms for direct algorithms of adjustment
* (7): iterative adjustment VII for tax runs based on peak CO2 emissions, with change of temporal tax profile after time of peak budget, aiming for net-zero thereafter, see core/postsolve.gms for direct algorithms of adjustment
* (9): [REMIND 2.1 default for validation peakBudget runs, in combination with carbonprice = diffCurvPhaseIn2Lin) ] aims at achieving [c_budgetCO2from2020] as peakBudget. Scales up and down the original CO2 price path before the peaking year; after the peaking year annual increase by [cm_taxCO2inc_after_peakBudgYr]. Automatically shifts [cm_peakBudgYr] to find the correct peaking year for a given .

**Description:**

"whether or not a tax or a budget target should be iteratively adjusted depending on actual emission or forcing level";



### cm_NDC_divergentScenario {-}

choose scenario about convergence of CO2eq prices in realization NDC of 45_carbonprice

```{r}
cfg$gms$cm_NDC_divergentScenario <- 0
```

**Possible Values:**

--

**Description:**

choose scenario about convergence of CO2eq prices in NDC realization of module [45_carbonprice]
(0) 70 years after 2030
(1) 120 years after 2030
(2) until year 3000 ("never")



### cm_co2_tax_2020 {-}

level of co2 tax in year 2020 in $ per t CO2eq, makes sense only for emiscen eq 9 and 45_carbonprice exponential

```{r}
cfg$gms$cm_co2_tax_2020 <- -1
```

**Possible Values:**

* (-1): default setting equivalent to no carbon tax
* (any number >= 0): tax level in 2020, with 5% exponential increase over time

**Description:**

--



### cm_co2_tax_growth {-}

yearly growth rate of co2 tax

```{r}
cfg$gms$cm_co2_tax_growth <- 1.05
```

**Possible Values:**

* (any number >= 0): rate of exponential increase over time

**Description:**

growth rate of carbon tax



### c_macscen {-}

use of mac

```{r}
cfg$gms$c_macscen <- 1
```

**Possible Values:**

* (1): on
* (2): off

**Description:**

--



### cm_nucscen {-}

nuclear option choice

```{r}
cfg$gms$cm_nucscen <- 2
```

**Possible Values:**

* (1): no fnrs, tnrs completely free after 2020
* (2): no fnrs, tnrs with restricted new builds until 2030 (based on current data on plants under construction, planned or proposed)
* (3): no tnrs no fnrs
* (4): fix at bau level
* (5): no new nuclear investments after 2020
* (6): +33% investment costs (tnrs) & uranium resources increased by a factor of 10

**Description:**

--



### cm_ccapturescen {-}

carbon capture option choice, no carbon capture only if CCS and CCU are switched off!

```{r}
cfg$gms$cm_ccapturescen <- 1
```

**Possible Values:**

* (1): yes
* (2): no carbon capture (only if CCS and CCU are switched off!)
* (3): no bio carbon capture
* (4): no carbon capture in the electricity sector

**Description:**

carbon capture option choice



### c_bioliqscen {-}

switch liquids producing technology on or off

```{r}
cfg$gms$c_bioliqscen <- 1
```

**Possible Values:**

* (0): no technologies
* (1): all technologies

**Description:**

bioenergy liquids technology choise



### c_bioh2scen {-}

switch hydrogen producing technology on or off

```{r}
cfg$gms$c_bioh2scen <- 1
```

**Possible Values:**

* (0): no technologies
* (1): all technologies

**Description:**

bioenergy hydrogen technology choice



### c_shGreenH2 {-}

lower bound on share of green hydrogen in all hydrogen by 2030

```{r}
cfg$gms$c_shGreenH2 <- 0
```

**Possible Values:**

* (a number between 0 and 1): share

**Description:**

--



### c_shBioTrans {-}

upper bound on share of bioliquids in transport from 2025 onwards

```{r}
cfg$gms$c_shBioTrans <- 1
```

**Possible Values:**

* (a number between 0 and 1): share

**Description:**

--



### cm_shSynTrans {-}

lower bound on share of synfuels in transport fuels by 2035

```{r}
cfg$gms$cm_shSynTrans <- 0
```

**Possible Values:**

* (a number between 0 and 1): share

**Description:**

lower bound on share of synthetic fuels in all transport fuels by 2045



### cm_shSynGas {-}

lower bound on share of synthetic gases by 2045

```{r}
cfg$gms$cm_shSynGas <- 0
```

**Possible Values:**

--

**Description:**

NA



### cm_IndCCSscen {-}

CCS for Industry

```{r}
cfg$gms$cm_IndCCSscen <- 1
```

**Possible Values:**

--

**Description:**

NA



### cm_optimisticMAC {-}

assume optimistic Industry MAC from AR5 Ch. 10?

```{r}
cfg$gms$cm_optimisticMAC <- 0
```

**Possible Values:**

--

**Description:**

NA



### cm_CCS_cement {-}

CCS for cement sub-sector

```{r}
cfg$gms$cm_CCS_cement <- 1
```

**Possible Values:**

--

**Description:**

NA



### cm_CCS_chemicals {-}

CCS for chemicals sub-sector

```{r}
cfg$gms$cm_CCS_chemicals <- 1
```

**Possible Values:**

--

**Description:**

NA



### cm_CCS_steel {-}

CCS for steel sub-sector

```{r}
cfg$gms$cm_CCS_steel <- 1
```

**Possible Values:**

--

**Description:**

NA



### c_solscen {-}

solar option choice

```{r}
cfg$gms$c_solscen <- 1
```

**Possible Values:**

* (1): yes
* (2): no solar
* (3): fix at bau level

**Description:**

--



### cm_bioenergy_tax {-}

level of bioenergy tax in fraction of bioenergy price

```{r}
cfg$gms$cm_bioenergy_tax <- 1.5
```

**Possible Values:**

* (0): default setting equivalent to no tax
* (any number >= 0): tax level, e.g. for a 100% tax [cm_bioenergy_tax] has to be 1

**Description:**

--



### cm_bioenergymaxscen {-}

bound on global pebiolc production excluding residues

```{r}
cfg$gms$cm_bioenergymaxscen <- 0
```

**Possible Values:**

* (0): no bound
* (1): 100 EJ global bioenergy potential (bound in boundsextra.inc)
* (2): 200 EJ global bioenergy potential (bound in boundsextra.inc)
* (3): 300 EJ global bioenergy potential (bound in boundsextra.inc)
* (4): 152 EJ global bioenergy potential, i.e. 100 EJ 2nd generation (bound in boundsextra.inc)
* (5): (placeholder for scenario from DIPOL branch that is not yet merged)
* (6): 75 EJ (2050) and 90 EJ (2100) global bioenergy potential (linear interpolation in between)

**Description:**

choose bound on global pebiolc production excluding residues
optional scaling of bioenergy costs in generisdata.inc (at the moment: no scaling for both cases)



### cm_tradecost_bio {-}

choose financal tradecosts for biomass (purpose grown pebiolc)

```{r}
cfg$gms$cm_tradecost_bio <- 2
```

**Possible Values:**

* (1): low   tradecosts (for other SSP scenarios than SSP2)
* (2): high  tradecosts (default and SSP2)

**Description:**

--



### cm_1stgen_phaseout {-}

choose if 1st generation biofuels should phase out after 2030 (deltacap=0)

```{r}
cfg$gms$cm_1stgen_phaseout <- 0
```

**Possible Values:**

* (0): 1st generation biofuels after 2020 are fixed at upper limit of resource potential (maxprod)
* (1): no new capacities for 1st generation biofuel technologies may be built after 2030 -> phaseout until ~2060

**Description:**

choose if 1st generation biofuels should phase out after 2030 (vm_deltaCap=0)



### cm_cprice_red_factor {-}

reduction factor for price on co2luc when calculating the revenues. Replicates the reduction applied in MAgPIE

```{r}
cfg$gms$cm_cprice_red_factor <- 1
```

**Possible Values:**

--

**Description:**

NA



### cm_GDPcovid {-}

switch to turn on short-term GDP loss by covid-19

```{r}
cfg$gms$cm_GDPcovid <- 0
```

**Possible Values:**

* (0):  off
* (1):  on

**Description:**

GDP correction for covid
*ML* emulates a schock, only feasible with start year 2020, don't use in calibration



### cm_startyear {-}

first optimized modelling time step [year]

```{r}
cfg$gms$cm_startyear <- 2005
```

**Possible Values:**

* (2005): standard for BAU to check if model is well calibrated
* (2015): standard for all policy runs (eq. to fix2010) and production baselines, especially if various baselines with varying parameters are explored
* (....): later start for delay policy runs, eg. 2025 for what used to be delay2020

**Description:**

"first free (or pseudo-free in case of 2005) modelling time step";



### c_start_budget {-}

start of GHG budget limit

```{r}
cfg$gms$c_start_budget <- 2100
```

**Possible Values:**

--

**Description:**

NA



### cm_prtpScen {-}

pure rate of time preference standard values

```{r}
cfg$gms$cm_prtpScen <- 3
```

**Possible Values:**

* (1): 1 %
* (3): 3 %

**Description:**

--



### cm_fetaxscen {-}

choice of final energy tax path, subsidy path and inconvenience cost path, values other than 0 make setting module 21_tax on

```{r}
cfg$gms$cm_fetaxscen <- 3
```

**Possible Values:**

* (0): no tax, sub, inconv
* (1): constant t,s,i (used in SSP 5 and ADVANCE WP3.1 HighOilSub)
* (2): converging tax, phased out sub (-2030), no inconvenience cost so far (used in SSP 1)
* (3): constant tax, phased out sub (-2050), no inconvenience cost so far (used in SSP 2)
* (4): constant tax, phased out sub (-2030), no inconvenience cost so far (used in SDP)

**Description:**

"choice of final energy tax path, subsidy path and inconvenience cost path, values other than 0 make setting module [21_tax] on";
*RP* even if set to 0, the PE inconvenience cost/SO2-cost for coal are always on if module [21_tax] is on



### cm_multigasscen {-}

scenario on GHG portfolio to be included in permit trading scheme

```{r}
cfg$gms$cm_multigasscen <- 2
```

**Possible Values:**

* (1): CO2 only
* (2): all GHG
* (3): all GHG excl CO2 emissions from LULUCF

**Description:**

--



### cm_permittradescen {-}

scenario assumption on permit trades

```{r}
cfg$gms$cm_permittradescen <- 1
```

**Possible Values:**

* (1): full permit trade (no restrictions)
* (2): no permit trade (only domestic mitigation)
* (3): limited trade (certain percentage of GDP)

**Description:**

scenario on permit trade
c_limit_peur_scen  "limit total uranium production"
(0): no
(1): yes (the exact amount is specified in boundsextra)



### cm_limit_peur_scen {-}

limit total uranium production

```{r}
cfg$gms$cm_limit_peur_scen <- 1
```

**Possible Values:**

* (0): off
* (1): on

**Description:**

--



### cm_rentdiscoil {-}

[grades2poly] discount factor for the oil rent

```{r}
cfg$gms$cm_rentdiscoil <- 0.2
```

**Possible Values:**

--

**Description:**

NA



### cm_rentdiscoil2 {-}

[grades2poly] discount factor for the oil rent achieved in 2100

```{r}
cfg$gms$cm_rentdiscoil2 <- 0.9
```

**Possible Values:**

--

**Description:**

NA



### cm_rentconvoil {-}

[grades2poly] number of years required to converge to the 2100 oil rent

```{r}
cfg$gms$cm_rentconvoil <- 50
```

**Possible Values:**

--

**Description:**

NA



### cm_rentdiscgas {-}

[grades2poly] discount factor for the gas rent

```{r}
cfg$gms$cm_rentdiscgas <- 0.6
```

**Possible Values:**

--

**Description:**

NA



### cm_rentdiscgas2 {-}

[grades2poly] discount factor for the gas rent achieved in 2100

```{r}
cfg$gms$cm_rentdiscgas2 <- 0.8
```

**Possible Values:**

--

**Description:**

NA



### cm_rentconvgas {-}

[grades2poly] number of years required to converge to the 2100 gas rent

```{r}
cfg$gms$cm_rentconvgas <- 50
```

**Possible Values:**

--

**Description:**

NA



### cm_rentdisccoal {-}

[grades2poly] discount factor for the coal rent

```{r}
cfg$gms$cm_rentdisccoal <- 0.4
```

**Possible Values:**

--

**Description:**

NA



### cm_rentdisccoal2 {-}

[grades2poly] discount factor for the coal rent achieved in 2100

```{r}
cfg$gms$cm_rentdisccoal2 <- 0.6
```

**Possible Values:**

--

**Description:**

NA



### cm_rentconvcoal {-}

[grades2poly] number of years required to converge to the 2100 coal rent

```{r}
cfg$gms$cm_rentconvcoal <- 50
```

**Possible Values:**

--

**Description:**

NA



### c_cint_scen {-}

additional GHG emissions from mining fossil fuels

```{r}
cfg$gms$c_cint_scen <- 1
```

**Possible Values:**

* (0): switch is off (emissions are not accounted)
* (1): switch is on (emissions are accounted)

**Description:**

--



### cm_so2tax_scen {-}

level of SO2 tax

```{r}
cfg$gms$cm_so2tax_scen <- 1
```

**Possible Values:**

* (0): so2 tax is set to zero
* (1): so2 tax is low
* (2): so2 tax is standard
* (3): so2 tax is high
* (4): so2 tax intermediary between 1 and 2, multiplying (1) tax by the ratio (3)/(2)

**Description:**

--



### cm_damage {-}

cm_damage factor for forcing overshoot

```{r}
cfg$gms$cm_damage <- 0.005
```

**Possible Values:**

--

**Description:**

*JeS* can be used to lower forcing overshoot in [cm_emiscen] 8 scenarios, use only with box model!



### cm_solwindenergyscen {-}

scenario for fluctuating renewables, 1 is reference, 2 is pessimistic with limits to fluctuating SE el share

```{r}
cfg$gms$cm_solwindenergyscen <- 1
```

**Possible Values:**

--

**Description:**

(0) advanced - cheap investment costs, higher learning rates for pv, csp and wind
(1) reference - normal investment costs & learning rates for pv, csp and wind     EMF27-3nd round Adv scenario
(2) pessimistic EMF27 and AWP 2 - share of PV, wind&CSP limited to 20%. Learning rates reduced by 20%, floor costs increased by 40%. EMF27-3nd round Cons scenario
(3) frozen - no learning after 2010, share of PV, wind&CSP limited to 20%. EMF27-3rd round Frozen scenario
(4) pessimistic SSP: pessimistic techno-economic assumptions



### c_techAssumptScen {-}

scenario for assumptions of energy technologies based on SSP scenarios, 1: SSP2 (default), 2: SSP1, 3: SSP5

```{r}
cfg$gms$c_techAssumptScen <- 1
```

**Possible Values:**

--

**Description:**

*JH* This flag defines an energy technology scenario
(1) SSP2: reference scenario - default investment costs & learning rates for pv, csp and wind
(2) SSP1: advanced renewable energy techno., pessimistic for nuclear and CCS
(3) SSP5: pessimistic techno-economic assumptions



### c_ccsinjecratescen {-}

CCS injection rate factor, 0.5% by default yielding a 60 Mt per year IR

```{r}
cfg$gms$c_ccsinjecratescen <- 1
```

**Possible Values:**

--

**Description:**

*JH* This flag determines the upper bound of the CCS injection rate
*LP* CCS refers to carbon sequestration, carbon capture is modelled separately
(0) no "CCS" as in no carbon sequestration at all
(1) reference case: 0.005
(2) lower estimate: 0.0025
(3) upper estimate: 0.075
(4) unconstrained: 1
(5) sustainability case: 0.001



### c_ccscapratescen {-}

CCS capture rate

```{r}
cfg$gms$c_ccscapratescen <- 1
```

**Possible Values:**

--

**Description:**

*JH*  This flag determines the CO2 capture rate of CCS technologies
(1) reference
(2) increased capture rate



### c_export_tax_scen {-}

choose which oil export tax is used in the model. 0 = none, 1 = fix

```{r}
cfg$gms$c_export_tax_scen <- 0
```

**Possible Values:**

--

**Description:**





### cm_gdximport_target {-}

whether or not the starting value for iteratively adjusted budgets, tax scenarios, or forcing targets (emiscen 5,6,8,9) should be read in from the input.gdx

```{r}
cfg$gms$cm_gdximport_target <- 0
```

**Possible Values:**

* (0): no import, the default starting value as specified in modules/[21_tax]/on/input/tax_CO2.inc, core/input/data_emibudget.inc, modules/[15_climate]/box/datainput.gms is used
* (1): the values from the gdx are read in (works only if the gdx has a parameter value) ATTENTION: make sure that the values from the gdx have the right structure (e.g. regionally differentiated or not)

**Description:**

"whether or not the starting value for iteratively adjusted budgets, tax scenarios, or forcing targets (emiscen 5,6,7,8,9) should be read in from the input.gdx";



### cm_gs_ew {-}

grain size (for enhanced weathering, CDR module) [micrometre]

```{r}
cfg$gms$cm_gs_ew <- 20
```

**Possible Values:**

--

**Description:**

NA



### cm_LimRock {-}

limit amount of rock spread each year [Gt]

```{r}
cfg$gms$cm_LimRock <- 1000
```

**Possible Values:**

--

**Description:**

NA



### c_tau_so2_xmpt {-}

switch for temporarily (mainly in the past) exempting chinese SO2 emissions from the SO2 tax

```{r}
cfg$gms$c_tau_so2_xmpt <- 0
```

**Possible Values:**

--

**Description:**

NA



### cm_expoLinear_yearStart {-}

time at which carbon price increases lineraly instead of exponentially

```{r}
cfg$gms$cm_expoLinear_yearStart <- 2050
```

**Possible Values:**

--

**Description:**

NA



### c_budgetCO2from2020FFI {-}

carbon budget for CO2 emissions starting from 2020 from FFI (in GtCO2)

```{r}
cfg$gms$c_budgetCO2from2020FFI <- 700
```

**Possible Values:**

--

**Description:**

NA



### c_budgetCO2from2020 {-}

cumulative CO2|Total emissions budget 2020-2100, Gt CO2

```{r}
cfg$gms$c_budgetCO2from2020 <- 1150
```

**Possible Values:**

--

**Description:**

carbon budget for all CO2 emissions starting from 2020 (in GtCO2)
budgets from AR6 for 2020-2100 (including 2020), for 1.5°C: 400 Gt CO2, for 2°C: 1150 Gt CO2



### c_abtrdy {-}

first year in which advanced bio-energy technology are ready (unit is year; e.g. 2050)

```{r}
cfg$gms$c_abtrdy <- 2010
```

**Possible Values:**

--

**Description:**

NA



### c_abtcst {-}

scaling of the cost of advanced bio-energy technologies (no unit, 50% increase means 1.5)

```{r}
cfg$gms$c_abtcst <- 1
```

**Possible Values:**

--

**Description:**

NA



### cm_postTargetIncrease {-}

carbon price increase per year after target is reached (€/tCO2)

```{r}
cfg$gms$cm_postTargetIncrease <- 2
```

**Possible Values:**

--

**Description:**

carbon price increase per year after target is reached (euro per tCO2)




### cm_DiscRateScen {-}

Implicit additional discount rate on investment in energy efficiency

```{r}
cfg$gms$cm_DiscRateScen <- 0
```

**Possible Values:**

--

**Description:**

Scenario for the implicit discount rate applied to the energy efficiency capital
(0) Baseline without higher discount rate: No additional discount rate
(1) Baseline with higher discount rate: Increase the discount rate by 10%pts from 2005 until the end
(2) Energy Efficiency policy: 10%pts higher discount rate until cm_start_year and 0 afterwards.
(3) Energy Efficiency policy: higher discount rate until cm_start_year and 25% of the initial value afterwards.
(4) Energy Efficiency policy: higher discount rate until cm_start_year, decreasing to 25% value linearly until 2030.



### cm_noReboundEffect {-}

Switch for allowing a rebound effect when closing the efficiency gap (cm_DiscRateScen)

```{r}
cfg$gms$cm_noReboundEffect <- 0
```

**Possible Values:**

--

**Description:**

NA



### cm_esubGrowth {-}

long term growth of the elasticity of substitution

```{r}
cfg$gms$cm_esubGrowth <- "middle"
```

**Possible Values:**

--

**Description:**

(low) 1.3
(middle) 1.5
(high) 2
specify regions to which nucscen, capturescen should apply to (e.g. [c_regi_nucscen] <- "JPN,USA")



### cm_trdcst {-}

parameter to scale trade export cost for gas

```{r}
cfg$gms$cm_trdcst <- 1.5
```

**Possible Values:**

--

**Description:**

NA



### cm_trdadj {-}

parameter scale the adjustment cost parameter for increasing gas trade export

```{r}
cfg$gms$cm_trdadj <- 2.0
```

**Possible Values:**

--

**Description:**

NA



### c_refcapbnd {-}

switch for fixing refinery capacities to the SSP2 levels in 2010 (if equal zero then no fixing)

```{r}
cfg$gms$c_refcapbnd <- 0
```

**Possible Values:**

--

**Description:**

NA



### cm_frac_CCS {-}

tax on CCS to reflect risk of leakage, formulated as fraction of ccs O&M costs

```{r}
cfg$gms$cm_frac_CCS <- 10
```

**Possible Values:**

--

**Description:**

NA



### cm_frac_NetNegEmi {-}

tax on CDR to reflect risk of overshooting, formulated as fraction of carbon price

```{r}
cfg$gms$cm_frac_NetNegEmi <- 0.5
```

**Possible Values:**

--

**Description:**

NA



### cm_peakBudgYr {-}

date of net-zero CO2 emissions for peak budget runs without overshoot

```{r}
cfg$gms$cm_peakBudgYr <- 2050
```

**Possible Values:**

--

**Description:**

time of net-zero CO2 emissions (peak budget), requires emiscen = 9 and [cm_iterative_target_adj] = 7, will potentially be adjusted by algorithms



### cm_taxCO2inc_after_peakBudgYr {-}

annual increase of CO2 price after the Peak Budget Year in $ per tCO2

```{r}
cfg$gms$cm_taxCO2inc_after_peakBudgYr <- 3
```

**Possible Values:**

--

**Description:**

NA



### cm_CO2priceRegConvEndYr {-}

Year at which regional CO2 prices converge in module 45 realization diffPhaseIn2LinFlex

```{r}
cfg$gms$cm_CO2priceRegConvEndYr <- 2050
```

**Possible Values:**

--

**Description:**

NA



### cm_flex_tax {-}

switch for flexibility tax/subsidy, switching it on activates a tax on a number of technologies with flexible or inflexible electricity input.

```{r}
cfg$gms$cm_flex_tax <- 0
```

**Possible Values:**

--

**Description:**

switch for enabling flexibility tax
technologies with flexible eletricity input get a subsidy corresponding to the lower-than-average electricity prices that they see, while
inflexible technologies get a tax corresponding to the higher-than-average electricity prices that they see
(0) flexibility tax off
(1) flexibility tax on



### cm_TaxConvCheck {-}

switch for enabling tax convergence check in nash mode

```{r}
cfg$gms$cm_TaxConvCheck <- 0
```

**Possible Values:**

--

**Description:**

- switches tax convergence check in nash mode on and off (check that tax revenue in all regions, periods be smaller than 0.01% of GDP)
0 (off)
1 (on), default



### cm_H2targets {-}

switches on capacity targets for electrolysis in NDC techpol following national Hydrogen Strategies

```{r}
cfg$gms$cm_H2targets <- 0
```

**Possible Values:**

--

**Description:**

NA



### cm_PriceDurSlope_elh2 {-}

slope of price duration curve of electrolysis

```{r}
cfg$gms$cm_PriceDurSlope_elh2 <- 20
```

**Possible Values:**

--

**Description:**

, slope of price duration curve for electrolysis (increase means more flexibility subsidy for electrolysis H2)



### cm_FlexTaxFeedback {-}

switch deciding whether flexibility tax feedback on buildlings and industry electricity prices is on

```{r}
cfg$gms$cm_FlexTaxFeedback <- 0
```

**Possible Values:**

--

**Description:**

, switches on feedback of flexibility tax on buildings/industry (electricity price decrease for electrolysis has to be matched by electrictiy price increase in buildings/industry)



### cm_build_H2costAddH2Inv {-}

additional h2 distribution costs for low diffusion levels (default value: 6.5$/ 100 /Kwh)

```{r}
cfg$gms$cm_build_H2costAddH2Inv <- 0.2
```

**Possible Values:**

--

**Description:**

<- additional h2 distribution costs for low diffusion levels (default value: 6.5$/kg = 0.2$/Kwh)



### cm_build_costDecayStart {-}

simplified logistic function end of full value (ex. 5%  -> between 0 and 5% the function will have the value 1). [%]

```{r}
cfg$gms$cm_build_costDecayStart <- 0.05
```

**Possible Values:**

--

**Description:**

<- 0.05 # simplified logistic function end of full value (ex. 5%  -> between 0 and 5% the function will have the value 1). [%]



### cm_build_H2costDecayEnd {-}

simplified logistic function start of null value (ex. 10% -> after 10% the function will have the value 0). [%]

```{r}
cfg$gms$cm_build_H2costDecayEnd <- 0.1
```

**Possible Values:**

--

**Description:**

<- 0.1  # simplified logistic function start of null value (ex. 10% -> after 10% the function will have the value 0). [%]



### cm_build_AdjCostActive {-}

Activate adjustment cost to penalise inter-temporal variation of area-specific weatherisation demand and space cooling efficiency slope (only in putty)

```{r}
cfg$gms$cm_build_AdjCostActive <- 0
```

**Possible Values:**

--

**Description:**

NA



### cm_indst_H2costAddH2Inv {-}

additional h2 distribution costs for low diffusion levels. [3.25$/ 0.1 /kWh]

```{r}
cfg$gms$cm_indst_H2costAddH2Inv <- 0.1
```

**Possible Values:**

--

**Description:**

<- 0.1  # additional h2 distribution costs for low diffusion levels. [3.25$/kg = 0.1$/kWh]



### cm_indst_costDecayStart {-}

simplified logistic function end of full value   (ex. 5%  -> between 0 and 5% the simplified logistic function will have the value 1). [%]

```{r}
cfg$gms$cm_indst_costDecayStart <- 0.05
```

**Possible Values:**

--

**Description:**

<- 0.05 # simplified logistic function end of full value   (ex. 5%  -> between 0 and 5% the simplified logistic function will have the value 1). [%]



### cm_indst_H2costDecayEnd {-}

simplified logistic function start of null value (ex. 10% -> between 10% and 100% the simplified logistic function will have the value 0). [%]

```{r}
cfg$gms$cm_indst_H2costDecayEnd <- 0.1
```

**Possible Values:**

--

**Description:**

<- 0.1  # simplified logistic function start of null value (ex. 10% -> between 10% and 100% the simplified logistic function will have the value 0). [%]



### cm_BioSupply_Adjust_EU {-}

factor for scaling sub-EU bioenergy supply curves

```{r}
cfg$gms$cm_BioSupply_Adjust_EU <- 3
```

**Possible Values:**

--

**Description:**

scales bioenergy supply curves in EU regions (mainly used to match EUR H12/Magpie bioenergy potential)



### cm_BioImportTax_EU {-}

factor for EU bioenergy import tax

```{r}
cfg$gms$cm_BioImportTax_EU <- 1
```

**Possible Values:**

--

**Description:**

NA



### cm_biotrade_phaseout {-}

switch for phaseing out biomass trade in the respective regions by 2030

```{r}
cfg$gms$cm_biotrade_phaseout <- 0
```

**Possible Values:**

--

**Description:**

NA



### cm_bioprod_histlim {-}

regional parameter to limit biomass (pebiolc.1) production to a multiple of the 2015 production

```{r}
cfg$gms$cm_bioprod_histlim <- -1
```

**Possible Values:**

--

**Description:**

NA



### cm_HeatLim_b {-}

switch to set maximum share of district heating in FE buildings

```{r}
cfg$gms$cm_HeatLim_b <- 1
```

**Possible Values:**

--

**Description:**

NA



### cm_ElLim_b {-}

switch to set maximum share of electricity in FE buildings

```{r}
cfg$gms$cm_ElLim_b <- 1
```

**Possible Values:**

--

**Description:**

NA



### cm_noPeFosCCDeu {-}

switch to suppress Pe2Se Fossil Carbon Capture in Germany

```{r}
cfg$gms$cm_noPeFosCCDeu <- 0
```

**Possible Values:**

--

**Description:**

NA



### cm_startIter_EDGET {-}

starting iteration of EDGE-T

```{r}
cfg$gms$cm_startIter_EDGET <- 14
```

**Possible Values:**

--

**Description:**

NA



### cm_INNOPATHS_priceSensiBuild {-}

Price sensitivity of energy carrier choice in buildings

```{r}
cfg$gms$cm_INNOPATHS_priceSensiBuild <- -3
```

**Possible Values:**

--

**Description:**

NA



### cm_logitCal_markup_conv_b {-}

value to which logit calibration markup of standard fe2ue technologies in detailed buildings module converges to

```{r}
cfg$gms$cm_logitCal_markup_conv_b <- 0.8
```

**Possible Values:**

--

**Description:**

NA



### cm_logitCal_markup_newtech_conv_b {-}

value to which logit calibration markup of new fe2ue technologies in detailed buildings module converges to

```{r}
cfg$gms$cm_logitCal_markup_newtech_conv_b <- 0.3
```

**Possible Values:**

--

**Description:**

NA



### cm_regipol_slope_beforeTarget {-}

--

```{r}
cfg$gms$cm_regipol_slope_beforeTarget <- "off"
```

**Possible Values:**

--

**Description:**

NA



### cm_VRE_supply_assumptions {-}

default (0), optimistic (1), sombre (2), or bleak (3) assumptions on VRE supply

```{r}
cfg$gms$cm_VRE_supply_assumptions <- 0
```

**Possible Values:**

--

**Description:**

NA



### c_CO2priceDependent_AdjCosts {-}

--

```{r}
cfg$gms$c_CO2priceDependent_AdjCosts <- "on"
```

**Possible Values:**

--

**Description:**

default "on" changes adjustment costs for advanced vehicles in dependence of CO2 prices



### cm_carbonprice_temperatureLimit {-}

not-to-exceed temperature target in degree above pre-industrial

```{r}
cfg$gms$cm_carbonprice_temperatureLimit <- 1.8
```

**Possible Values:**

--

**Description:**

NA



### cm_damages_BurkeLike_specification {-}

empirical specification for Burke-like damage functions

```{r}
cfg$gms$cm_damages_BurkeLike_specification <- 0
```

**Possible Values:**

--

**Description:**

NA



### cm_damages_BurkeLike_persistenceTime {-}

persistence time in years for Burke-like damage functions

```{r}
cfg$gms$cm_damages_BurkeLike_persistenceTime <- 30
```

**Possible Values:**

--

**Description:**

NA



### cm_damages_SccHorizon {-}

Horizon for SCC calculation. Damages cm_damagesSccHorizon years into the future are internalized.

```{r}
cfg$gms$cm_damages_SccHorizon <- 100
```

**Possible Values:**

--

**Description:**

NA



### cm_deuCDRmax {-}

switch to limit maximum annual CDR amount in Germany in MtCO2 per y

```{r}
cfg$gms$cm_deuCDRmax <- -1
```

**Possible Values:**

--

**Description:**

NA



### c_BaselineAgriEmiRed {-}

switch to lower agricultural base line emissions as fraction of standard assumption, a value of 0.25 will lower emissions by a fourth

```{r}
cfg$gms$c_BaselineAgriEmiRed <- 0
```

**Possible Values:**

--

**Description:**

NA





# GAMS Compiler Flags




## General


### cm_MAgPIE_coupling {-}

switch on coupling mode with MAgPIE

```{r}
cfg$gms$cm_MAgPIE_coupling <- "off"
```

**Possible Values:**

* (off): off = REMIND expects to be run standalone (emission factors are used, shiftfactors are set to zero)
* (on): on  = REMIND expects to be run based on a MAgPIE reporting file (emission factors are set to zero because emissions are retrieved from the MAgPIE reporting, shift factors for supply curves are calculated)

**Description:**

--



### cm_rcp_scen {-}

chooses RCP scenario

```{r}
cfg$gms$cm_rcp_scen <- "none"
```

**Possible Values:**

* (none): no RCP scenario, standard setting
* (rcp20): RCP2.0
* (rcp26): RCP2.6
* (rcp37): RCP3.7
* (rcp45): RCP4.5
* (rcp60): RCP6.0
* (rcp85): RCP8.5

**Description:**

--



### cm_NDC_version {-}

data version of nationally determined contributions (NDC) UNFCCC database

```{r}
cfg$gms$cm_NDC_version <- "2022_cond"
```

**Possible Values:**

* (2022_cond):   all NDCs conditional to international financial support
* (2022_uncond): all NDCs independent of international financial support
* (2021_cond):   all NDCs conditional to international financial support published until December 31, 2021
* (2021_uncond): all NDCs independent of international financial support published until December 31, 2021
* (2018_cond):   all NDCs conditional to international financial support published until December 31, 2018
* (2018_uncond): all NDCs independent of international financial support published until December 31, 2018

**Description:**

choose version year of NDC targets as well as conditional vs. unconditional targets



### cm_CO2TaxSectorMarkup {-}

CO2 tax markup in buildings or transport sector, a value of 0.5 means CO2 tax increased by 50%

```{r}
cfg$gms$cm_CO2TaxSectorMarkup <- "off"
```

**Possible Values:**

* (off): no markup
* (GLO.build 1, USA_regi.trans 0.25, EUR_regi.trans 0.25): "example for CO2 tax markup in transport of 25% in USA and EUR, and CO2eq tax markup in buildings sector of 100 % in all regions. Currently, build and trans are the only two elements of the set emi_sectors that are supported."

**Description:**

--



### cm_secondary_steel_bound {-}

--

```{r}
cfg$gms$cm_secondary_steel_bound <- "scenario"
```

**Possible Values:**

--

**Description:**

NA



### c_regi_earlyreti_rate {-}

maximum portion of capital stock that can be retired in one year for a region

```{r}
cfg$gms$c_regi_earlyreti_rate <- "GLO 0.09, EUR_regi 0.15"
```

**Possible Values:**

--

**Description:**

GLO 0.09, EUR_regi 0.15: default value. (0.09 means full retirement after 11 years, 10% standing after 10 years)



### c_tech_earlyreti_rate {-}

maximum portion of capital stock that can be retired in one year for a technology in a region

```{r}
cfg$gms$c_tech_earlyreti_rate <- "GLO.(biodiesel 0.14, bioeths 0.14), EUR_regi.(biodiesel 0.15, bioeths 0.15), USA_regi.pc 0.13, REF_regi.pc 0.13, CHA_regi.pc 0.13"
```

**Possible Values:**

--

**Description:**

maximum portion of capital stock that can be retired in one year for a region for a technology
GLO.(biodiesel 0.14, bioeths 0.1), EUR_regi.(biodiesel 0.15, bioeths 0.15), USA_regi.pc 0.13, REF_regi.pc 0.13, CHA_regi.pc 0.13: default value, including retirement of 1st gen biofuels, higher rate of coal phase-out for USA, REF and CHA



### cm_LU_emi_scen {-}

choose emission baseline for CO2, CH4, and N2O land use emissions from MAgPIE

```{r}
cfg$gms$cm_LU_emi_scen <- "SSP2"
```

**Possible Values:**

* (SSP1): emissions (from SSP1 scenario in MAgPIE)
* (SSP2): emissions (from SSP2 scenario in MAgPIE)
* (SSP5): emissions (from SSP5 scenario in MAgPIE)

**Description:**

--



### cm_tradbio_phaseout {-}

Switch that allows for a faster phase out of traditional biomass

```{r}
cfg$gms$cm_tradbio_phaseout <- "default"
```

**Possible Values:**

* (default):  Default assumption, reaching zero demand in 2100
* (fast):     Fast phase out, starting in 2025 reaching zero demand in 2070 (close to zero in 2060)

**Description:**

--



### cm_POPscen {-}

Population growth scenarios from UN data and IIASA projection used in SSP

```{r}
cfg$gms$cm_POPscen <- "pop_SSP2EU"
```

**Possible Values:**

--

**Description:**

pop_SSP1    "SSP1 population scenario"
pop_SSP2    "SSP2 population scenario"
pop_SSP3    "SSP3 population scenario"
pop_SSP4    "SSP4 population scenario"
pop_SSP5    "SSP5 population scenario"



### cm_GDPscen {-}

assumptions about future GDP development, linked to population development (cm_POPscen)

```{r}
cfg$gms$cm_GDPscen <- "gdp_SSP2EU"
```

**Possible Values:**

* (gdp_SSP1):  SSP1 fastGROWTH medCONV
* (gdp_SSP2):  SSP2 medGROWTH medCONV
* (gdp_SSP3):  SSP3 slowGROWTH slowCONV
* (gdp_SSP4):  SSP4  medGROWTH mixedCONV
* (gdp_SSP5):  SSP5 fastGROWTH fastCONV

**Description:**

--



### cm_demScen {-}

--

```{r}
cfg$gms$cm_demScen <- "gdp_SSP2EU"
```

**Possible Values:**

--

**Description:**

NA



### cm_oil_scen {-}

assumption on oil availability

```{r}
cfg$gms$cm_oil_scen <- "medOil"
```

**Possible Values:**

* (lowOil): low
* (medOil): medium (this is the new case)
* (highOil): high (formerly this has been the "medium" case; RoSE relevant difference)
* (4): very high (formerly this has been the "high" case; RoSE relevant difference)

**Description:**

--



### cm_gas_scen {-}

assumption on gas availability

```{r}
cfg$gms$cm_gas_scen <- "medGas"
```

**Possible Values:**

* (lowGas): low
* (medGas): medium
* (highGas): high

**Description:**

--



### cm_coal_scen {-}

assumption on coal availability

```{r}
cfg$gms$cm_coal_scen <- "medCoal"
```

**Possible Values:**

* (0): very low (this has been the "low" case; RoSE relevant difference)
* (lowCoal): low (this is the new case)
* (medCoal): medium
* (highCoal): high

**Description:**

--



### c_SSP_forcing_adjust {-}

--

```{r}
cfg$gms$c_SSP_forcing_adjust <- "forcing_SSP2"
```

**Possible Values:**

--

**Description:**

"chooses forcing target and budget according to SSP scenario such that magicc forcing meets the target";
("forcing_SSP1") settings consistent with SSP 1
("forcing_SSP2") settings consistent with SSP 2
("forcing_SSP5") settings consistent with SSP 5



### c_delayPolicy {-}

--

```{r}
cfg$gms$c_delayPolicy <- "SPA0"
```

**Possible Values:**

--

**Description:**

NA



### cm_regiExoPrice {-}

set exogenous co2 tax path for specific regions using a switch, require regipol module to be set to regiCarbonPrice (e.g. GLO.(2025 38,2030 49,2035 63,2040 80,2045 102,2050 130,2055 166,2060 212,2070 346,2080 563,2090 917,2100 1494,2110 1494,2130 1494,2150 1494) )

```{r}
cfg$gms$cm_regiExoPrice <- "off"
```

**Possible Values:**

--

**Description:**





### cm_regiCO2target {-}

budget or year target for specific region or region group. Ex.: '2050.EUR_regi.budget 72, 2050.DEU.year 0.1' sets a 72 GtCO2eq budget target for European countries for emissions between 2020 and 2050, and a 100 MtCO2 CO2eq emission target for the 2050 year for Germany (only used if regipol model regiCarbonPrice realization is active)

```{r}
cfg$gms$cm_regiCO2target <- "off"
```

**Possible Values:**

--

**Description:**





### cm_quantity_regiCO2target {-}

emissions quantity upper bound from specific year for region group. Ex.: '2050.EUR_regi.netGHG 0.000001, obliges European GHG emissions to be zero from 2050 on

```{r}
cfg$gms$cm_quantity_regiCO2target <- "off"
```

**Possible Values:**

--

**Description:**





### cm_emiMktETS {-}

enable European ETS specific carbon prices. off = disabled (default); number = percentage of 2005 emissions allowance for 2050 (ex. 0.1 = 2050 emissions correspond to 10% of the 2005 emissions)

```{r}
cfg$gms$cm_emiMktETS <- "off"
```

**Possible Values:**

--

**Description:**





### cm_emiMktETS_type {-}

--

```{r}
cfg$gms$cm_emiMktETS_type <- "off"
```

**Possible Values:**

--

**Description:**

off = disabled (default); "budget" = ETS 2013-2050 budget target based on linear decrease up to 2005 emissions multiplied by [cm_emiMktETS] in 2050; "year" = ETS 2050 emissions equal to 2005 emissions multiplied by [cm_emiMktETS]



### cm_ETS_postTargetIncrease {-}

ETS carbon price increase per year after the year target and before 2055 (linear string or euro per tCO2)

```{r}
cfg$gms$cm_ETS_postTargetIncrease <- "linear"
```

**Possible Values:**

--

**Description:**





### cm_ETS_post2055Increase {-}

ETS carbon price increase per year after 2055 (euro per tCO2)

```{r}
cfg$gms$cm_ETS_post2055Increase <- 2
```

**Possible Values:**

--

**Description:**





### cm_emiMktES {-}

--

```{r}
cfg$gms$cm_emiMktES <- "off"
```

**Possible Values:**

--

**Description:**

"enable European Effort Sharing specific carbon prices. off = disabled (default); 1 = target per region follows EU per country legislation targets; other number (1.2, 0.9,...) = target in 2030 is multiplied by the factor (1.2 = achieved target in 2030 is 20% higher than the predicted by the EU legislation)



### cm_emiMktES_type {-}

emissions type that the target is calaculated for. netGHG = GHG emissions target (default), netCO2 = CO2 emissions target

```{r}
cfg$gms$cm_emiMktES_type <- "netGHG"
```

**Possible Values:**

--

**Description:**





### cm_ESD_postTargetIncrease {-}

ESD carbon price increase per year after the year target and before 2055 (euro per tCO2)

```{r}
cfg$gms$cm_ESD_postTargetIncrease <- 8
```

**Possible Values:**

--

**Description:**





### cm_ESD_post2055Increase {-}

ESD carbon price increase per year after 2055 (euro per tCO2)

```{r}
cfg$gms$cm_ESD_post2055Increase <- 2
```

**Possible Values:**

--

**Description:**





### cm_emiMktEScoop {-}

--

```{r}
cfg$gms$cm_emiMktEScoop <- "off"
```

**Possible Values:**

--

**Description:**

NA



### cm_emiMktES2020price {-}

--

```{r}
cfg$gms$cm_emiMktES2020price <- 30
```

**Possible Values:**

--

**Description:**

NA



### cm_emiMktES2050 {-}

--

```{r}
cfg$gms$cm_emiMktES2050 <- "off"
```

**Possible Values:**

--

**Description:**

NA



### cm_NucRegiPol {-}

enable European region specific nuclear phase-out and new capacitiy constraints

```{r}
cfg$gms$cm_NucRegiPol <- "off"
```

**Possible Values:**

--

**Description:**





### cm_CoalRegiPol {-}

enable European region specific coal phase-out and new capacitiy constraints

```{r}
cfg$gms$cm_CoalRegiPol <- "off"
```

**Possible Values:**

--

**Description:**





### cm_proNucRegiPol {-}

enable European region specific pro nuclear capacitiy constraints

```{r}
cfg$gms$cm_proNucRegiPol <- "off"
```

**Possible Values:**

--

**Description:**





### cm_CCSRegiPol {-}

def = off, year for earliest investment in Europe, with one timestep split between countries currently exploring - Norway (NEN), Netherlands (EWN) and UK (UKI) - and others

```{r}
cfg$gms$cm_CCSRegiPol <- "off"
```

**Possible Values:**

--

**Description:**





### cm_implicitFE {-}

--

```{r}
cfg$gms$cm_implicitFE <- "off"
```

**Possible Values:**

--

**Description:**

"off, FEtarget or exoTax (def = off). FEtarget calculates endogenously the tax necessary to comply with the final energy targets (defined at [cm_implFETarget]). exoTax sets an exogenous tax at stationary and/or transportation level to represent non CO2 price policies (defined at [cm_implFEExoTax]).



### cm_implFETarget {-}

default = 2030.EUR_regi 1.26921. Only active if cm_implicitFE = FEtarget. Enforce EU Energy Efficiency Directive maximum final energy level of 956 Mtoe by 2030 for EU28 regions by exogenous taxes reflecting non price-driven measures, i.e. not influencing the carbon pricing -> 956 Mtoe (956 Mtoe -> 956 * 10^6 toe -> 956 * 10^6 toe * 41.868 GJ/toe -> 40025.808 * 10^6 GJ * 10^-9 EJ/GJ -> 40.025808 EJ * 1 TWa/31.536 EJ -> 1.26921 TWa)

```{r}
cfg$gms$cm_implFETarget <- "2030.EUR_regi 1.26921"
```

**Possible Values:**

--

**Description:**





### cm_implFEExoTax {-}

default = off. Value to overwrite default defined in the parameter p47_implFEExoTax, ex. "2040.EUR_regi.stat 5, 2050.EUR_regi.stat 10, 2030.EUR_regi.trans 15, 2040.EUR_regi.trans 30, 2050.EUR_regi.trans 40". Only active if cm_implicitFE = exoTax. Sets a FE tax on stationary sectors (industry plus buldings) of 5$/GJ from 2040 onward, and 10$/GJ from 2050 onward; Sets a FE tax on transportation of 15$/GJ from 2030 onward, and 30$/GJ from 2040 onward, and 40$/GJ from 2040 onward.

```{r}
cfg$gms$cm_implFEExoTax <- "off"
```

**Possible Values:**

--

**Description:**





### cm_vehiclesSubsidies {-}

default = off. If "on" applies country specific BEV and FCEV subsidies from 2020 onwards

```{r}
cfg$gms$cm_vehiclesSubsidies <- "off"
```

**Possible Values:**

--

**Description:**





### cm_dispatchSetyDown {-}

--

```{r}
cfg$gms$cm_dispatchSetyDown <- "off"
```

**Possible Values:**

--

**Description:**

NA



### cm_dispatchSeelDown {-}

--

```{r}
cfg$gms$cm_dispatchSeelDown <- "off"
```

**Possible Values:**

--

**Description:**

NA



### c_CES_calibration_iterations {-}

--

```{r}
cfg$gms$c_CES_calibration_iterations <- 10
```

**Possible Values:**

--

**Description:**

NA



### c_CES_calibration_new_structure {-}

--

```{r}
cfg$gms$c_CES_calibration_new_structure <- 0
```

**Possible Values:**

--

**Description:**

NA



### c_CES_calibration_write_prices {-}

--

```{r}
cfg$gms$c_CES_calibration_write_prices <- 0
```

**Possible Values:**

--

**Description:**

NA



### cm_CES_calibration_default_prices {-}

--

```{r}
cfg$gms$cm_CES_calibration_default_prices <- 0.01
```

**Possible Values:**

--

**Description:**

NA



### c_CES_calibration_industry_FE_target {-}

--

```{r}
cfg$gms$c_CES_calibration_industry_FE_target <- 1
```

**Possible Values:**

--

**Description:**

NA



### cm_calibration_string {-}

def = off, else = additional string to include in the calibration name to be used

```{r}
cfg$gms$cm_calibration_string <- "off"
```

**Possible Values:**

--

**Description:**





### c_testOneRegi_region {-}

--

```{r}
cfg$gms$c_testOneRegi_region <- "EUR"
```

**Possible Values:**

--

**Description:**

NA



### cm_cooling_shares {-}

--

```{r}
cfg$gms$cm_cooling_shares <- "dynamic"
```

**Possible Values:**

--

**Description:**

use "static" or "dynamic" cooling shares in module [70_water]/heat



### cm_techcosts {-}

--

```{r}
cfg$gms$cm_techcosts <- "REG"
```

**Possible Values:**

--

**Description:**

use regionalized or globally homogenous technology costs for certain technologies



### cm_regNetNegCO2 {-}

--

```{r}
cfg$gms$cm_regNetNegCO2 <- "on"
```

**Possible Values:**

--

**Description:**

default "on" allows for regionally netNegative CO2 emissions, setting "off" activates bound in core/bounds.gms that disallows net negative CO2 emissions at the regional level



### c_regi_nucscen {-}

regions to apply nucscen to

```{r}
cfg$gms$c_regi_nucscen <- "all"
```

**Possible Values:**

--

**Description:**





### c_regi_capturescen {-}

region to apply ccapturescen to

```{r}
cfg$gms$c_regi_capturescen <- "all"
```

**Possible Values:**

--

**Description:**





### c_regi_sensscen {-}

regions which regional sensitivity parameters apply to

```{r}
cfg$gms$c_regi_sensscen <- "all"
```

**Possible Values:**

--

**Description:**

: specify regions to which certain regional sensitivity parameters should be applied to
applied to sensitivity parameters
cfg$gms$[cm_EDGEtr_scen]  "the EDGE-T scenario"
("Conservative_liquids") very conservative scenario with high reliance on fossil fuels in the transport sector
("Electricity_push") vehicles with electric drivetrains get some initial push on shares and preferences, leads to ~70% takeover by 2050
("Hydrogen_push") similar to the "Electricity_push" scenario, but FCEV penetration is much less as FCEVs remain rather expensive.
("Smart_lifestyles_Electricity_push") similar to "Electricity_push" but with reduced overall demand and increased acceptance of small cars, busses and trains.



### cm_EDGEtr_scen {-}

--

```{r}
cfg$gms$cm_EDGEtr_scen <- "Mix"
```

**Possible Values:**

--

**Description:**

NA



### cm_import_EU {-}

EU switch for different scenarios of EU SE import assumptions

```{r}
cfg$gms$cm_import_EU <- "off"
```

**Possible Values:**

--

**Description:**

NA



### cm_altFeEmiFac {-}

--

```{r}
cfg$gms$cm_altFeEmiFac <- "off"
```

**Possible Values:**

--

**Description:**

<- "off"  # def <- "off", regions that should use alternative data from "umweltbundesamt" on emission factors for final energy carriers (ex. "EUR_regi, NEU_regi")
c_deuCDRmax  <- -1 switch to cap annual DEU CDR amount by value assigned to switch, or no cap if -1, in MtCO2
-------------------- flags --------------------------------------------------



### cm_calibration_FE {-}

--

```{r}
cfg$gms$cm_calibration_FE <- "off"
```

**Possible Values:**

--

**Description:**

overwritte default fe trajectories with low, medium and high alternatives for buildings, transport and industry



### cm_INNOPATHS_eni {-}

--

```{r}
cfg$gms$cm_INNOPATHS_eni <- "off"
```

**Possible Values:**

--

**Description:**

NA



### cm_INNOPATHS_enb {-}

--

```{r}
cfg$gms$cm_INNOPATHS_enb <- "off"
```

**Possible Values:**

--

**Description:**

NA



### cm_INNOPATHS_LDV_mkt_share {-}

--

```{r}
cfg$gms$cm_INNOPATHS_LDV_mkt_share <- "off"
```

**Possible Values:**

--

**Description:**

NA



### cm_share_LDV_sales {-}

--

```{r}
cfg$gms$cm_share_LDV_sales <- "off"
```

**Possible Values:**

--

**Description:**

NA



### cm_INNOPATHS_incolearn {-}

--

```{r}
cfg$gms$cm_INNOPATHS_incolearn <- "off"
```

**Possible Values:**

--

**Description:**

NA



### cm_INNOPATHS_storageFactor {-}

--

```{r}
cfg$gms$cm_INNOPATHS_storageFactor <- "off"
```

**Possible Values:**

--

**Description:**

NA



### cm_learnRate {-}

--

```{r}
cfg$gms$cm_learnRate <- "off"
```

**Possible Values:**

--

**Description:**

NA



### cm_INNOPATHS_adj_seed {-}

--

```{r}
cfg$gms$cm_INNOPATHS_adj_seed <- "off"
```

**Possible Values:**

--

**Description:**

NA



### cm_INNOPATHS_adj_seed_cont {-}

--

```{r}
cfg$gms$cm_INNOPATHS_adj_seed_cont <- "off"
```

**Possible Values:**

--

**Description:**

NA



### cm_INNOPATHS_adj_coeff {-}

--

```{r}
cfg$gms$cm_INNOPATHS_adj_coeff <- "off"
```

**Possible Values:**

--

**Description:**

NA



### cm_INNOPATHS_adj_coeff_cont {-}

--

```{r}
cfg$gms$cm_INNOPATHS_adj_coeff_cont <- "off"
```

**Possible Values:**

--

**Description:**

NA



### cm_INNOPATHS_adj_seed_multiplier {-}

--

```{r}
cfg$gms$cm_INNOPATHS_adj_seed_multiplier <- "off"
```

**Possible Values:**

--

**Description:**

NA



### cm_INNOPATHS_adj_coeff_multiplier {-}

--

```{r}
cfg$gms$cm_INNOPATHS_adj_coeff_multiplier <- "off"
```

**Possible Values:**

--

**Description:**

NA



### cm_INNOPATHS_inco0Factor {-}

--

```{r}
cfg$gms$cm_INNOPATHS_inco0Factor <- "off"
```

**Possible Values:**

--

**Description:**

NA



### cm_INNOPATHS_CCS_markup {-}

--

```{r}
cfg$gms$cm_INNOPATHS_CCS_markup <- "off"
```

**Possible Values:**

--

**Description:**

NA



### cm_INNOPATHS_Industry_CCS_markup {-}

--

```{r}
cfg$gms$cm_INNOPATHS_Industry_CCS_markup <- "off"
```

**Possible Values:**

--

**Description:**

NA



### cm_INNOPATHS_renewables_floor_cost {-}

--

```{r}
cfg$gms$cm_INNOPATHS_renewables_floor_cost <- "off"
```

**Possible Values:**

--

**Description:**

NA



### cm_INNOPATHS_DAC_eff {-}

--

```{r}
cfg$gms$cm_INNOPATHS_DAC_eff <- "off"
```

**Possible Values:**

--

**Description:**

NA



### cm_INNOPATHS_sehe_upper {-}

--

```{r}
cfg$gms$cm_INNOPATHS_sehe_upper <- "off"
```

**Possible Values:**

--

**Description:**

NA



### cm_INNOPATHS_pushCalib {-}

--

```{r}
cfg$gms$cm_INNOPATHS_pushCalib <- "none"
```

**Possible Values:**

--

**Description:**

NA



### cm_INNOPATHS_reducCostB {-}

--

```{r}
cfg$gms$cm_INNOPATHS_reducCostB <- "none"
```

**Possible Values:**

--

**Description:**

NA



### cm_INNOPATHS_effHP {-}

--

```{r}
cfg$gms$cm_INNOPATHS_effHP <- 5
```

**Possible Values:**

--

**Description:**

NA



### cm_CESMkup_build {-}

switch for setting markup cost to CES nodes in buildings

```{r}
cfg$gms$cm_CESMkup_build <- "standard"
```

**Possible Values:**

--

**Description:**

NA



### cm_CESMkup_ind {-}

switch for setting markup cost to CES nodes in industry

```{r}
cfg$gms$cm_CESMkup_ind <- "standard"
```

**Possible Values:**

--

**Description:**

NA



### cm_feShareLimits {-}

--

```{r}
cfg$gms$cm_feShareLimits <- "off"
```

**Possible Values:**

--

**Description:**

<-   "off"  # def <- "off", limit the electricity final energy share to be in line with the industry maximum electrification levels (60% by 2050 in the electric scenario), 10% lower (=50% in 2050) in an increased efficiency World, or 20% lower (40% in 2050) in an incumbents future (incumbents). The incumbents scenario also limits a minimal coverage of buildings heat provided by gas and liquids (25% by 2050).



### cm_ARIADNE_FeShareBounds {-}

switch for minimum share of liquids and gases for industry needed for the ARIADNE project

```{r}
cfg$gms$cm_ARIADNE_FeShareBounds <- "off"
```

**Possible Values:**

--

**Description:**

NA



### cm_ariadne_VRECapFac_adj {-}

switch for enabling increase of VRE capacity factors for wind and solar PV in Germany until 2040 in line with ARIADNE assumptions

```{r}
cfg$gms$cm_ariadne_VRECapFac_adj <- "off"
```

**Possible Values:**

--

**Description:**

NA



### c_VREPot_Factor {-}

switch for rescaling renewable potentials in all grades which have not been used by 2020

```{r}
cfg$gms$c_VREPot_Factor <- "off"
```

**Possible Values:**

--

**Description:**

NA



### cm_FEtax_trajectory_abs {-}

switch for setting the aboslute FE tax level explicitly from a given year onwards, before tax levels increases or decreases linearly to that value

```{r}
cfg$gms$cm_FEtax_trajectory_abs <- "off"
```

**Possible Values:**

--

**Description:**

NA



### cm_FEtax_trajectory_rel {-}

factor for scaling the FE tax level relative to cm_startyear from a given year onwards, before tax levels increases or decreases linearly to that value

```{r}
cfg$gms$cm_FEtax_trajectory_rel <- "off"
```

**Possible Values:**

--

**Description:**

NA



### cm_wind_offshore {-}

--

```{r}
cfg$gms$cm_wind_offshore <- 1
```

**Possible Values:**

--

**Description:**

= 1, wind energy is represented by "wind" and "windoff", where "wind" means wind onshore. Later this will be the default and the name "wind" will be made to change to windon



### cm_SlowConvergence {-}

--

```{r}
cfg$gms$cm_SlowConvergence <- "off"
```

**Possible Values:**

--

**Description:**

off       !! def = off
*RP* Turn on a slower convergence scheme where each conopt file is used twice, thus conopt1 is used for itr 1+2, conopt.op2 for itr 3+4, conopt.op3 for itr 5+6, conopt.op4 for itr 7+8, conopt.op5 from itr 9 on.
*RP* from my own experience, this improves convergence and actually decreases total runtime, even if you start from a gdx with good convergence. But, as always, feelings about REMIND runtimes can be misleading :-)



### cm_nash_mode {-}

--

```{r}
cfg$gms$cm_nash_mode <- "parallel"
```

**Possible Values:**

--

**Description:**

NA



### cm_debug_preloop {-}

--

```{r}
cfg$gms$cm_debug_preloop <- "off"
```

**Possible Values:**

--

**Description:**

NA



### cm_OILRETIRE {-}

--

```{r}
cfg$gms$cm_OILRETIRE <- "on"
```

**Possible Values:**

--

**Description:**

on           !! def = on
*RP* Flag to allow the model to not extract oil, even though the eq_fuelex_dec would force it to extract.



### cm_INCONV_PENALTY {-}

--

```{r}
cfg$gms$cm_INCONV_PENALTY <- "on"
```

**Possible Values:**

--

**Description:**

on     !! def = on
*RP* 2012-03-06 Flag to turn on inconvenience penalties, e.g. for air pollution



### cm_INCONV_PENALTY_FESwitch {-}

--

```{r}
cfg$gms$cm_INCONV_PENALTY_FESwitch <- "on"
```

**Possible Values:**

--

**Description:**

off     !! def = off
flag to trun on inconvenience penalty to avoid switching shares on buildings, transport and industry biomass use if costs are relatively close (seLiqbio, sesobio, segabio)



### cm_so2_out_of_opt {-}

--

```{r}
cfg$gms$cm_so2_out_of_opt <- "on"
```

**Possible Values:**

--

**Description:**

on       !! def = on
*JeS* Flag to exclude aerosols from optimization routine, should be used especially for temperature targets



### cm_MOFEX {-}

--

```{r}
cfg$gms$cm_MOFEX <- "off"
```

**Possible Values:**

--

**Description:**

off    !! def=off
*JH/LB* Activate MOFEX partial fossil fuel extraction cost minimization model
* Warning: Use a well-converged run since the model uses vm_prodPe from the input GDX
cfg$gms$[c_skip_output]            <- "off"    # def <- off
Skip output? (Useful for development)
cfg$gms$[cm_ccsfosall]             <- "off"    # def <- off



### cm_less_TS {-}

--

```{r}
cfg$gms$cm_less_TS <- "on"
```

**Possible Values:**

--

**Description:**

NA



### c_skip_output {-}

--

```{r}
cfg$gms$c_skip_output <- "off"
```

**Possible Values:**

--

**Description:**

off
*** This flag turns off output production
ap_scenarios  off!! def = off
*JeS* Report aerosol and precursor emissions using exogenous emission factor scenarios



### cm_ccsfosall {-}

--

```{r}
cfg$gms$cm_ccsfosall <- "off"
```

**Possible Values:**

--

**Description:**

NA



### cm_APscen {-}

--

```{r}
cfg$gms$cm_APscen <- "SSP2"
```

**Possible Values:**

--

**Description:**

NA



### cm_Full_Integration {-}

--

```{r}
cfg$gms$cm_Full_Integration <- "off"
```

**Possible Values:**

--

**Description:**

use "on" to treat wind and solar as fully dispatchable electricity production technologies



### c_scaleEmiHistorical {-}

--

```{r}
cfg$gms$c_scaleEmiHistorical <- "on"
```

**Possible Values:**

--

**Description:**

NA



### cm_magicc_calibrateTemperature2000 {-}

--

```{r}
cfg$gms$cm_magicc_calibrateTemperature2000 <- "uncalibrated"
```

**Possible Values:**

--

**Description:**

NA



### cm_magicc_config {-}

--

```{r}
cfg$gms$cm_magicc_config <- "OLDDEFAULT"
```

**Possible Values:**

--

**Description:**

NA



### cm_magicc_temperatureImpulseResponse {-}

--

```{r}
cfg$gms$cm_magicc_temperatureImpulseResponse <- "off"
```

**Possible Values:**

--

**Description:**

NA



### cm_damage_DiceLike_specification {-}

--

```{r}
cfg$gms$cm_damage_DiceLike_specification <- "HowardNonCatastrophic"
```

**Possible Values:**

--

**Description:**

NA



### cm_conoptv {-}

--

```{r}
cfg$gms$cm_conoptv <- "conopt3"
```

**Possible Values:**

--

**Description:**

NA



### test_TS {-}

--

```{r}
cfg$gms$test_TS <- "off"
```

**Possible Values:**

--

**Description:**

*LB* default: 5 years time steps from 2005 to 2150
*LB* [test_TS]: 2005,2010, 2020,2030,2040,2050,2070,2090,2110,2130,2150
*LB* [cm_less_TS]: 2005,2010,2015,2020,2025,2030,2035,2040,2045,2050,2055,2060,2070,2080,2090,2100,2110,2130,2150
*LB* [END2110]: 2005:5:2105,2120



### END2110 {-}

--

```{r}
cfg$gms$END2110 <- "off"
```

**Possible Values:**

--

**Description:**

*LB* default: 5 years time steps from 2005 to 2150
*LB* [test_TS]: 2005,2010, 2020,2030,2040,2050,2070,2090,2110,2130,2150
*LB* [cm_less_TS]: 2005,2010,2015,2020,2025,2030,2035,2040,2045,2050,2055,2060,2070,2080,2090,2100,2110,2130,2150
*LB* [END2110]: 2005:5:2105,2120



